\subsection{Motors}\label{ssec:motors}
In order for the autonomous car to physically move itself, it would need some motors.
As described in \todo{Autoref to requirements section, stating that the car must be realistic (meaning motor to forward and to steer)} the car will need a motor to drive it forward and backwards, as well as a motor, in order to steer the car in a direction.

In addition to the motors, which will be elaborated herein, other motors are also available.
These motors include different DC looking motors, which are powered and controlled through two power wires.
However, since no model name or other information could be found for these motors, it's not possible to find the specifications for these.
Therefore, these motors will not be described further.

The motors will be selected, in \autoref{ssec:choiceOfHardware}, based upon the following criteria:
\begin{itemize}
  \item By default the motors should be able to, without any unauthorized changes, to be connected to and controlled by the chosen platform, on which no unauthorized changes may be made.
  \item Precision is prioritized, when choosing the motor that drives the car, as well as the motor that steers it, in order to control the car accurately.
  \item In the selection of the motor, to drive the autonomous car forward and backwards, a sufficiently powerful motor is prioritized, so that the weight of the car is not limited by the motor power.
  \item For the choice of the steering motor, speed is somewhat prioritized, in order to change direction quickly.
\end{itemize}
